\renewcommand{\abstractname}{\Huge\bfseries Abstract}
\begin{abstract}
Because of the development of Wi-Fi and WLAN technology, wireless network services made an evolution in the recent time. Most of the time of people´s daily life is taking part inside large indoor environments, such as office room, library, shopping malls, concert hall and airport. These crowded places increase the risk for the public safety. For this reason the positioning technology is in the focus of attention. This technique has a broad prospect and develops very fast. The significance of its research is most important now.

This thesis introduces the application of design and implementation about "Guidance System" based on Wi-Fi technology and SNMP, by a practical web service for Mobile devices in WWW environments. It has the advantage, the application runs on mobile terminal without any additional software or APP, it requires only the web browser.


\textbf{Keywords}: \textbf{Routing SNMP Locating WLAN Wi-Fi Positioning }

\end{abstract}

\renewcommand{\abstractname}{\Huge\bfseries Abstrakt}
\begin{abstract}
Aufgrund der rasanten Entwicklung der Wi-Fi und WLAN-Technologie, basierend auf den Wireless-Netzwerkdiensten haben sich neue Entwicklungen gezeigt. Das Leben der Menschen findet in der meisten Zeit in gro\ss{}en Indoor-Umgebungen wie B\"uroraum, Bibliothek, Einkaufszentren, Konzertsaal und Flughafen statt. Die \"uberf\"ullten Orte werden das Risiko f\"ur den Menschen erh\"ohen und die \"offentliche Sicherheit mehr gef\"ahrden. Daher hat die Positionierungstechnologie immer im Mittelpunkt der Aufmerksamkeit gestanden. 

Diese Technik hat eine gro\ss{}e Perspektive und entwickelt sich sehr schnell. Die Bedeutung der Studie ist sehr gro\ss{}.

In dieser These wird die Anwendung der Konzeption und Umsetzung vom "Guidance System" basierend auf Wi-Fi-Technologie und SNMP demonstriert, durch einen praktischen Web-Service f\"ur Mobilger\"ate in WWW Umgebungen.

Es hat den Vorteil, die Anwendung l\"auft auf mobilen Endger\"aten, ohne zus\"atzliche Software oder APP und erfordert nur den Web-Browser.

\textbf{Schlagw\"orter}: \textbf{Wegf\"uhrung} \textbf{Routing SNMP Locating WLAN Wi-Fi Positioning}
\end{abstract}