https://en.wikipedia.org/wiki/Social_networking_service
https://en.wikipedia.org/wiki/Friendster
https://en.wikipedia.org/wiki/Facebook
https://en.wikipedia.org/wiki/Twitter
 P.  Resnick  and  H.  R.  Varian.  Recommender  Systems[J].  Communications  of  the  ACM, 1997, 40(3): 56-58. 
D. Goldberg, D. Nichols, B. M. Oki and D. Terry. Using Collaborative Filtering to Weave an Information Tapestry[J]. Communications of the ACM, 1992, 35(12): 61-70. 
 M. Balabanovic. An adaptive Web Page Recommendation Service[C]. In: Proceedings of the  first  International  Conference  on  Autonomous  Agents,  New  York,  USA,  1997: 378-385. 
 Pei-Shan Chang, I-Hsien Ting and Shyue-Liang Wang. Towards Social Recommendation System  Based  on  The  Data  From  Microblogs[C].  In:  Proceedings  of  the  International Conference  on  Advances  in  Social  Networks  Analysis  and  Mining(ASONAM), Kaohsiung, 2011: 672-677. 
     9.   I-Hsing Ting, Pei Shan Chang, and Shyue-Liang Wang. Understanding Microblog Users for Social Recommendation Based on Social Networks Analysis[J]. Journal of Universal Computer Science, 2012, 18(4): 554-576. 
  10. Ricardo  Baeza-Yates  and  Berthier  Ribeiro-Neto.  Modern  Information  Retrieval[M]. 
Addison-Wesley, 1999. 
    11. NJ  Belkin  and  WB  Croft.  Information  filtering  and  information  retrieval[J].  
Communications of the ACM , 1992, 35(12): 29-37. 
17. Bing Liu. Web Data Mining [ M]. Second Edition. Chicago, USA: Springer-Verlag,2009:211-229.
181. Fabian Abel, Qi Gao, Geert-Jan Houben, et al. Analyzing User Modeling on Twitter for Personalized News Recommendations [A] / / Proceedings of the 19th International Conference [ C]. Girona, Spain:UMAP,2011:1-12.
141. https://flink.apache.org/

[401] 
[501] G.Salton, C.Buckley. Term-weighting approaches in automatic text retrieval. Information Processing & Management, 1988, 24(5): 513-523.
601 .8.L Page, S Brin, R Motwani, T Winograd The PageRank citation ranking: bringing order to the web. Stanford University.1999
701 .Mihalcea R, Tarau P. TextRank: Bringing order into texts.Conference on Empirical Methods in Natural Language Processing(EMNLP-04).2004
801.Palshikar G K.Keyword Extraction from a Single Document Using Centrality Measures. The 2nd international conference on Pattern recognition and machine intelligence.2007

@article{SaltonYang1973,
	author = {G.Salton, C.S.Yang},
	title = {On the specification of term values in automatic indexing},
	journaltitle = {Journal of Documentation},
	date = {1973, 29(4): 351-372},
}
901. Ercan G, Ciceki I.Using lexical chains for keyword extraction.Information Processing and Management. 2007.